---
title: "Pakistan Poliovirus Population Immunity"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(rgeos)
library(maptools)
library(ggplot2)
library(mapproj)
source("C:/Files/Polio/Pakistan/Scripts/PAK_SIAD_Data_Prep.R")
source("C:/Files/Polio/Pakistan/Scripts/PAK_Function_plotggMap.R")


```

####This page is a example of an R Markdown page, using Pakistan Poliovirus Population Immunity as an example.


####Immunity trends since 2001
We estimate immunity (probability of protection against paralysis) for each non-polio AFP case between age 6 to 59 months using reported OPV dose history and the history of polio vaccination campaigns in each case's district of residence.
Below, the avegage immunity is plotted over time for the whole country.
```{r, fig.width = 6, fig.height = 3}
temp = aggregate(n[101], n[109], mean, na.rm=T)
ggplot(temp, aes(x=year.6mo, y=type1_immunity)) + geom_line() + geom_point() + 
  labs(y="Mean Type 1 Immunity",x="Six-Month Interval") + 
  scale_y_continuous(limit=c(0,1)) + theme_prefered()
```

####District immunity estimates 
In order to estimate population immunity at the district-level, we smoothed estimates using a spatiotemporal model to reduce noise arising from small samples sizes (each district often has less than 10 NP-AFP cases in a six-month interval).
Below, a histogram of smoothed district immunity estimates from 2014.
```{r, fig.width = 3.5, fig.height = 3}
ggplot(preds[preds$year==2014,], aes(x=type1_immunity)) + geom_histogram(binwidth=.05) +
  labs(x="Estimated Type 1 Immunity", y="District Count") + theme_prefered()
```

Below, the same values plotted on a map. The high vulnerability in North Waziristan is stands out clearly.
```{r, echo=F, fig.width = 7, fig.height = 6}
plt <- plotggMap(data=preds[preds$year==2014,], var.name="type1_immunity",id.var.name="index", brewer.cols=brewer.pal(9,"RdYlGn"), na.col="grey50", 
             legend.title="Type 1\nImmunity", main.title=NULL, map=district, var.limits=c(0,1), breaks=seq(0,1,.2), legend.pos=NA) #c(.93,.35)
plt 
```

